Changes in Mobility and Site Occupation during the Late Pleistocene in Korea

### 2019-12-20 analysis/paper/paper.Rmd
push before pull the current version
Revert "push before pull the current version"
This reverts commit b886a526bb85c54a9252cce442603792babeff94.

```{r setup, include=FALSE}
suppressMessages(library(tidyverse))
library(glue)
library(ggrepel)
library(here)

@@

```
# Introduction

@@

```{r}
# we'll use googlesheets package to get the data more efficiently
library(googlesheets)

# here is the key to the google sheet: this ggole sheet is same as kasa. so I could do kas_sites <- kasa 
kas_sites <- gs_key("14G0Mp-YSsKBOBPF1Z1zPWQbZQ-sjJSWLetDIQSlbsjw")

# get the tab names from this sheet: But that I couldn't use gs_ws_ls
kas_sites_names <- gs_ws_ls(kas_sites)

# sheets we need here
sheets <- c( "general_info",    "assemblage_info" )

# get the data from the tabs in this sheet!
kas_sites_sheets <- 
  map(sheets, ~kas_sites %>% gs_read_listfeed(ws = .x))
```

>>>>

```{r setup, include=FALSE}
suppressPackageStartupMessages(library(tidyverse))
library(glue)
library(ggrepel)
library(here)

@@

# join artefact type freqs with site data

kasa %>% 
  pivot_longer(-X, 
               names_to = "site_name",
               values_to = "count") %>% 
  pivot_wider(names_from = "X",
              values_from = "count") %>% 
  left_join(mydata)

# Introduction

@@
